Stability and accuracy of free surface time integration in buoyancy driven viscous flows

### 2016-04-29 free-surface-paper.tex
Add some text on the time evolution of the timescale.

\subsection{Numerical determination of $\tau_\mathrm{min}$}

@@

\begin{itemize}
\item Direct solution of Equation~\eqref{eq:generalized_eigenvalue}. This can be expensive, although
only the minimum relaxation time is required. For certain geometries a simple power iteration on 
the standard eigenvalue problem (Equation~\eqref{eq:standard_eigenvalue}) could be enough.
\item Analytical formulae. Several geometry and viscosity model combinations have analytical solutions
for relaxation spectra. Even if the user's model is not precisely the same (e.g., has some lateral viscosity
variations), an analytical approximation may be sufficient.
\item Scaling. In general, we expect the relaxation times to scale with $\tau \sim \frac{\eta}{\rho g L}$,
where the density, gravity, viscosity, and lengthscale $L$ are all representative values.  A small amount
of experimentation near this value of $\tau$ can find an appropriate relaxation time.
\item Observation of instabilities.  The mere act of observing a sloshing instability in an unstabilized
problem can furnish an estimate of its relaxation time.
\end{itemize}

>>>>

\subsection{Numerical determination of $\tau_\mathrm{min}$}
\label{sec:numerical_determination}

@@

\begin{itemize}
\item Direct solution of Equation~\eqref{eq:generalized_eigenvalue}. Solution of the whole spectrum is expensive,
however only the minimum relaxation time is required. For certain geometries a simple power iteration on 
the standard eigenvalue problem (Equation~\eqref{eq:standard_eigenvalue}) can be enough.
\item Analytical formulae. Several geometry and viscosity model combinations have analytical solutions
for relaxation spectra. Even if the user's model is not precisely the same (e.g., has some lateral viscosity
variations), an analytical approximation may be sufficient.
\item Scaling. In general, we expect the relaxation times to scale with $\tau \sim \frac{\eta}{\rho g L}$,
where the density, gravity, viscosity, and lengthscale $L$ are all representative values.  A small amount
of experimentation near this value of $\tau$ can find an appropriate relaxation time.
\end{itemize}

The first point deserves a bit more attention, since it provides the most general method for determining $\tau_\mathrm{min}$.
We discussed the numerical determination of $\tau_\mathrm{min}$ in Section~\ref{sec:numerical_determination}
by solving Equation~\eqref{eq:standard_eigenvalue} via power iteration.
Each iteration requires a solution of the Stokes system (the $C$ matrix), and we have found
that $\sim$10 iterations is usually enough to obtain a reasonable estimate of $\tau_\mathrm{min}$.
This can be done during preprocessing, so over the course of the simulation the cost of determining
$\tau_\mathrm{min}$ would be negligible.

As a simulation progresses, there is the possibility that its viscosity or density structure
will change, and as such its minimum relaxation time will evolve.
This, of course, means that the best choice of $\tau^*$ can change over the course of a simulation.
If $\tau_\mathrm{min}$ does not change significantly, the initial estimate can be fine.
Otherwise, one can periodically check the evolution and redetermine $\tau_\mathrm{min}$ by 
solving~\eqref{eq:standard_eigenvalue} during the model run.

In section \label{sec:results} we show examples of the numerical solution of $\tau_\mathrm{min}$
and its evolution in time.
